\vspace{-0.5cm} XSGRB - The X-shooter GRB afterglow sample

### 2018-10-16 document/referee_response.txt

#
# ------------------- Referee report
#
# This report presents a review of the article "The X-shooter GRB
# afterglow legacy sample (XS-GRB)" by Selsing and collaborators. The
# authors present and make available to the community a complete sample
# of GRB afterglows observed with the X-Shooter spectrograph on the VLT.
# This dataset is remarkable in several respect (>100 spectra available
# taken over 8 years) and some of these have not be published elsewhere.
# However, there are a number of important issues regarding both the
# scientific measurements and their presentation which are detailed
# below. These concerns need to be addressed before the paper can be
# considered for publication. More details on these points together with
# other comments are provided below.
#
# #
# # #
# Major Concerns:
#
# - One aspect of these data that needs more emphasis is the intervening
# absorbers. The data presented in this paper present a remarkable
# number of metal and HI intervening absorbers as can be judged from
# reading the appendix. These deserve much more attention, including a
# table listing their redshifts, column density measurements when
# available, metal lines detected, etc. A figure with their redshift
# distribution would also be very welcome. In addition, it would be
# interesting to compare the properties of this population with the
# absorbers towards background quasars.
#

This paper is meant as a general introduction of the XSGRB legacy sample
and constitutes the first in a series of papers. While we certainly
agree that the issue of intervening absorbers is an interesting one, we
feel that it is best treated in a dedicated publication, which we have
already published Christensen et al., A&A, 608A, 84C, 2017,
(arXiv:1709.01084) and are working on de Ugarte Postigo et al. in
prep.). These papers contain the complete list of intervening
systems, as well as linelists, redshifts, EWs, etc..

@@

Regarding the flux calibration accuracy, we have added a new section
($3.5). This includes a new way to correct for slit losses and tries to
assess the flux accuracy of the spectra presented. The paper has
significantly benefited from this suggestion.

# - The comparison of N(HI) distributions between intervening quasar
# absorbers and intrinsic GRB absorbers is not direct. The measurement
# of the column density of a system in the case of a quasar absorber
# integrate across the whole system. Conversely, in the case of GRBs,
# the burst event takes place at a random position in the host galaxy
# and in fact, on average, the column density will measure over only
# half of the system. This geometric effect should be taken into
# account.

This is certainly true, when comparing QSO DLAs to GRB DLA. We have
updated the figure and text surrounding Fig. 10 to reflect this. For
Fig. 9, where we are comparing GRB DLAs to GRB DLA, we have retained the
original values for N_HI.

# - Another concern is to do with using absorption features to measure
# the redshift. Indeed, one cannot exclude that the absorption is not at
# the position of host galaxy but lying in front of it. For this reason,
# the redshifts provided should be seen as upper limits.

We agree with the referee that, in principle, our values should be
considered as lower limits. We contend, though, that in the large
majority of cases the values we measured correspond to the actual
redshift of the GRB. We have added a paragraph in the text explaining
why this is.

# #
# Other Concerns:
#
# - the links to the actual data seem to be inactive. It is important to
# be able to review the material which is made available to the
# community.

### 2018-10-16 document/authorlist.tex
Last commit before Arxiv submission
Adding co-author suggestions

\author{
J.~Selsing \inst{1}$^,$\thanks{\email{jselsing@dark-cosmology.dk}}
\addtocounter{footnote}{2}
\and D.~Malesani \inst{1, 2, 3}\fnmsep\thanks{On-call observer}
\and P.~Goldoni \inst{4}\fnmsep$^\dagger$
\and J.~P.~U. Fynbo \inst{1, 2}\fnmsep$^\dagger$
\and T.~Kr\"{u}hler \inst{5}\fnmsep$^\dagger$
\and L.~A.~Antonelli \inst{6}\fnmsep$^\dagger$
\and M.~Arabsalmani \inst{7, 8}
\and J.~Bolmer \inst{5, 9}\fnmsep$^\dagger$
\and Z.~Cano \inst{10}\fnmsep$^\dagger$
\and L.~Christensen \inst{1}
\and S.~Covino \inst{11}\fnmsep$^\dagger$
\and P.~D'Avanzo \inst{11}\fnmsep$^\dagger$
\and V.~D'Elia \inst{12}\fnmsep$^\dagger$
\and A.~De~Cia \inst{13}
\and A.~de~Ugarte~Postigo \inst{1, 10}\fnmsep$^\dagger$
\and H.~Flores \inst{14}\fnmsep$^\dagger$
\and M.~Friis \inst{15, 16}
\and A.~Gomboc \inst{17}
\and J.~Greiner \inst{5}
\and P.~Groot \inst{18}
\and F.~Hammer \inst{14}
\and O.E.~Hartoog \inst{19}\fnmsep$^\dagger$
\and K.~E.~Heintz \inst{1, 2, 20}\fnmsep$^\dagger$
\and J.~Hjorth \inst{1}\fnmsep$^\dagger$
\and P.~Jakobsson \inst{20}\fnmsep$^\dagger$
\and J.~Japelj \inst{19}\fnmsep$^\dagger$
\and D.~A.~Kann \inst{10}\fnmsep$^\dagger$
\and L.~Kaper \inst{19}
\and C.~Ledoux \inst{9}
\and G.~Leloudas \inst{1}
\and A.J.~Levan \inst{21}\fnmsep$^\dagger$
\and E.~Maiorano \inst{22}
\and A.~Melandri \inst{11}\fnmsep$^\dagger$
\and B.~Milvang-Jensen \inst{1, 2}
\and E.~Palazzi \inst{22}
\and J.~T.~Palmerio \inst{23}\fnmsep$^\dagger$
\and D.~A.~Perley \inst{24}\fnmsep$^\dagger$
\and E.~Pian \inst{22}
\and S. ~Piranomonte \inst{6}\fnmsep$^\dagger$
\and G.~Pugliese \inst{19}\fnmsep$^\dagger$
\and R.~S\'{a}nchez-Ram\'{\i}rez \inst{25}\fnmsep$^\dagger$
\and S.~Savaglio \inst{26}
\and P.~Schady \inst{5}
\and S.~Schulze \inst{27}\fnmsep$^\dagger$
\and J.~Sollerman \inst{28}
\and M.~Sparre \inst{29}\fnmsep$^\dagger$
\and G.~Tagliaferri \inst{11}
\and N.~R.~Tanvir \inst{30}\fnmsep$^\dagger$
\and C.~C.~Th\"{o}ne \inst{10}
\and S.D.~Vergani \inst{14}\fnmsep$^\dagger$
\and P.~Vreeswijk \inst{18, 26}\fnmsep$^\dagger$
\and D.~Watson \inst{1, 2}\fnmsep$^\dagger$
\and K.~Wiersema \inst{21, 30}\fnmsep$^\dagger$
\and R.~Wijers \inst{19}
\and D.~Xu \inst{31}\fnmsep$^\dagger$
\and T.~Zafar \inst{32}
}

\institute{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 K\o benhavn \O, Denmark %1
%\and Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 K\o benhavn \O, Denmark
\and The Cosmic Dawn Center, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 K\o benhavn \O, Denmark
\and DTU Space, National Space Institute, Technical University of Denmark, Elektrovej 327, 2800 Lyngby, Denmark
\and APC, Astroparticule et Cosmologie, Universit\'e Paris Diderot, CNRS/IN2P3, CEA/Irfu, Observatoire de Paris, Sorbonne Paris Cit\'e, 10, Rue Alice Domon et L\'eonie Duquet, 75205, Paris Cedex 13, France
\and Max-Planck-Institut f\"{u}r extraterrestrische Physik, Giessenbachstra\ss e, 85748 Garching, Germany
\and INAF - Osservatorio Astronomico di Roma, Via Frascati 33, 00078, Monte Porzio Catone (Roma), Italy
\and IRFU, CEA, Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France
\and Universit\'e Paris Diderot, AIM, Sorbonne Paris Cit\'e, CEA, CNRS, F-91191 Gif-sur-Yvette, France
\and European Southern Observatory, Alonso de C\'{o}rdova 3107, Vitacura, Casilla 19001, Santiago 19, Chile
\and Instituto de Astrof\'isica de Andaluc\'ia (IAA-CSIC), Glorieta de la Astronom\'ia s/n, E-18008, Granada, Spain. % 10
%
\and INAF - Osservatorio Astronomico di Brera, via Bianchi 46, 23807, Merate (LC), Italy
\and Space Science Data Center - Agenzia Spaziale Italiana, via del Politecnico, s.n.c., I-00133, Roma, Italy
\and European Southern Observatory, Karl-Schwarzschild Str. 2, 85748 Garching bei M\”unchen, Germany
\and GEPI, Observatoire de Paris, PSL University, CNRS, 5 place Jules Janssen 92195, Meudon, France
\and KTH Royal Institute of Technology, Department of Physics, 106 91 Stockholm, Sweden
\and The Oskar Klein Centre for Cosmoparticle Physics, AlbaNova University Centre, 106 91 Stockholm, Sweden
\and Center for Astrophysics and Cosmology, University of Nova Gorica, Vipavska 11c, 5270 Ajdov\v s\v cina, Slovenia
\and Department of Astrophysics, IMAPP, Radboud University Nijmegen, PO Box 9010, 6500 GL Nijmegen, the Netherlands
\and Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, the Netherlands
\and Centre for Astrophysics and Cosmology, Science Institute, University of Iceland, Dunhagi 5, 107, Reykjavik, Iceland
\and Department of Physics, University of Warwick, Coventry, CV4 7AL, UK % 20
%
\and IASF/INAF Bologna, via Piero Gobetti 101, 40129 Bologna, Italy
\and Sorbonne Universit\'e, CNRS, UMR7095, Institut d'Astrophysique de Paris, F-75014, Paris, France
\and Astrophysics Research Institute, Liverpool John Moores University, IC2, Liverpool Science Park, 146 Brownlow Hill, Liverpool L3 5RF, UK
\and INAF, Istituto Astrofisica e Planetologia Spaziali, Via Fosso del Cavaliere 100, I-00133 Roma, Italy
\and Physics Department, University of Calabria, I-87036 Arcavacata di Rende, Italy
\and Department of Particle Physics and Astrophysics, Weizmann Institute of Science, 234 Herzl Street, Rehovot, 761000, Israel
\and Department of Astronomy, Stockholm University, AlbaNova, 10691 Stockholm, Sweden 
\and Institut f\"ur Physik und Astronomie, Universit\"at Potsdam, Karl-Liebknecht-Str.\,24/25, 14476 Golm, Germany
\and Department of Physics and Astronomy, University of Leicester, University Road, Leicester, LE1 7RH, United Kingdom
\and CAS Key Laboratory of Space Astronomy and Technology, National Astronomical Observatories, Chinese Academy of Sciences, Beijing, 100012, P.R. China % 30
%
\and Australian Astronomical Observatory, PO Box 915, North Ryde, NSW 1670, Australia.
}

>>>>

\author{
J.~Selsing \inst{1}$^,$\thanks{\email{jselsing@dark-cosmology.dk}}\addtocounter{footnote}{2}
\and D.~Malesani \inst{1, 2, 3}\fnmsep\thanks{On-call observer}
\and P.~Goldoni \inst{4}\fnmsep$^\dagger$
\and J.~P.~U. Fynbo \inst{1, 2}\fnmsep$^\dagger$
\and T.~Kr\"{u}hler \inst{5}\fnmsep$^\dagger$
\and L.~A.~Antonelli \inst{6}\fnmsep$^\dagger$
\and M.~Arabsalmani \inst{7, 8}
\and J.~Bolmer \inst{5, 9}\fnmsep$^\dagger$
\and Z.~Cano \inst{10}\fnmsep$^\dagger$
\and L.~Christensen \inst{1}
\and S.~Covino \inst{11}\fnmsep$^\dagger$
\and P.~D'Avanzo \inst{11}\fnmsep$^\dagger$
\and V.~D'Elia \inst{12}\fnmsep$^\dagger$
\and A.~De~Cia \inst{13}
\and A.~de~Ugarte~Postigo \inst{1, 10}\fnmsep$^\dagger$
\and H.~Flores \inst{14}\fnmsep$^\dagger$
\and M.~Friis \inst{15, 16}
\and A.~Gomboc \inst{17}
\and J.~Greiner \inst{5}
\and P.~Groot \inst{18}
\and F.~Hammer \inst{14}
\and O.E.~Hartoog \inst{19}\fnmsep$^\dagger$
\and K.~E.~Heintz \inst{1, 2, 20}\fnmsep$^\dagger$
\and J.~Hjorth \inst{1}\fnmsep$^\dagger$
\and P.~Jakobsson \inst{20}\fnmsep$^\dagger$
\and J.~Japelj \inst{19}\fnmsep$^\dagger$
\and D.~A.~Kann \inst{10}\fnmsep$^\dagger$
\and L.~Kaper \inst{19}
\and C.~Ledoux \inst{9}
\and G.~Leloudas \inst{1}
\and A.J.~Levan \inst{21}\fnmsep$^\dagger$
\and E.~Maiorano \inst{22}
\and A.~Melandri \inst{11}\fnmsep$^\dagger$
\and B.~Milvang-Jensen \inst{1, 2}
\and E.~Palazzi \inst{22}
\and J.~T.~Palmerio \inst{23}\fnmsep$^\dagger$
\and D.~A.~Perley \inst{24}\fnmsep$^\dagger$
\and E.~Pian \inst{22}
\and S. ~Piranomonte \inst{6}\fnmsep$^\dagger$
\and G.~Pugliese \inst{19}\fnmsep$^\dagger$
\and R.~S\'{a}nchez-Ram\'{\i}rez \inst{25}\fnmsep$^\dagger$
\and S.~Savaglio \inst{26}
\and P.~Schady \inst{5}
\and S.~Schulze \inst{27}\fnmsep$^\dagger$
\and J.~Sollerman \inst{28}
\and M.~Sparre \inst{29}\fnmsep$^\dagger$
\and G.~Tagliaferri \inst{11}
\and N.~R.~Tanvir \inst{30}\fnmsep$^\dagger$
\and C.~C.~Th\"{o}ne \inst{10}
\and S.D.~Vergani \inst{14}\fnmsep$^\dagger$
\and P.~Vreeswijk \inst{18, 26}\fnmsep$^\dagger$
\and D.~Watson \inst{1, 2}\fnmsep$^\dagger$
\and K.~Wiersema \inst{21, 30}\fnmsep$^\dagger$
\and R.~Wijers \inst{19}
\and D.~Xu \inst{31}\fnmsep$^\dagger$
\and T.~Zafar \inst{32}
}
\institute{Dark Cosmology Centre, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 K\o benhavn \O, Denmark %1
\and The Cosmic Dawn Center, Niels Bohr Institute, University of Copenhagen, Juliane Maries Vej 30, 2100 K\o benhavn \O, Denmark
\and DTU Space, National Space Institute, Technical University of Denmark, Elektrovej 327, 2800 Lyngby, Denmark
\and APC, Astroparticule et Cosmologie, Universit\'e Paris Diderot, CNRS/IN2P3, CEA/Irfu, Observatoire de Paris, Sorbonne Paris Cit\'e, 10, Rue Alice Domon et L\'eonie Duquet, 75205, Paris Cedex 13, France
\and Max-Planck Institut f\"{u}r extraterrestrische Physik, Giessenbachstra\ss e 1, 85748 Garching, Germany
\and INAF - Osservatorio Astronomico di Roma, Via Frascati 33, 00078, Monte Porzio Catone (Roma), Italy
\and IRFU, CEA, Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France
\and Universit\'e Paris Diderot, AIM, Sorbonne Paris Cit\'e, CEA, CNRS, F-91191 Gif-sur-Yvette, France
\and European Southern Observatory, Alonso de C\'{o}rdova 3107, Vitacura, Casilla 19001, Santiago 19, Chile
\and Instituto de Astrof\'isica de Andaluc\'ia (IAA-CSIC), Glorieta de la Astronom\'ia s/n, E-18008, Granada, Spain. % 10
\and INAF - Osservatorio Astronomico di Brera, via Bianchi 46, 23807, Merate (LC), Italy
\and Space Science Data Center - Agenzia Spaziale Italiana, via del Politecnico, s.n.c., I-00133, Roma, Italy
\and European Southern Observatory, Karl-Schwarzschild Str. 2, 85748 Garching bei M\"unchen, Germany
\and GEPI, Observatoire de Paris, PSL University, CNRS, 5 place Jules Janssen 92195, Meudon, France
\and KTH Royal Institute of Technology, Department of Physics, 106 91 Stockholm, Sweden
\and The Oskar Klein Centre for Cosmoparticle Physics, AlbaNova University Centre, 106 91 Stockholm, Sweden
\and Center for Astrophysics and Cosmology, University of Nova Gorica, Vipavska 11c, 5270 Ajdov\v s\v cina, Slovenia
\and Department of Astrophysics, IMAPP, Radboud University Nijmegen, PO Box 9010, 6500 GL Nijmegen, the Netherlands
\and Anton Pannekoek Institute for Astronomy, University of Amsterdam, Science Park 904, 1098 XH Amsterdam, the Netherlands
\and Centre for Astrophysics and Cosmology, Science Institute, University of Iceland, Dunhagi 5, 107, Reykjavik, Iceland
\and Department of Physics, University of Warwick, Coventry, CV4 7AL, UK % 20
\and IASF/INAF Bologna, via Piero Gobetti 101, 40129 Bologna, Italy
\and Sorbonne Universit\'e, CNRS, UMR7095, Institut d'Astrophysique de Paris, F-75014, Paris, France
\and Astrophysics Research Institute, Liverpool John Moores University, IC2, Liverpool Science Park, 146 Brownlow Hill, Liverpool L3 5RF, UK
\and INAF, Istituto Astrofisica e Planetologia Spaziali, Via Fosso del Cavaliere 100, I-00133 Roma, Italy
\and Physics Department, University of Calabria, I-87036 Arcavacata di Rende, Italy
\and Department of Particle Physics and Astrophysics, Weizmann Institute of Science, 234 Herzl Street, Rehovot, 761000, Israel
\and Department of Astronomy, Stockholm University, AlbaNova, 10691 Stockholm, Sweden 
\and Institut f\"ur Physik und Astronomie, Universit\"at Potsdam, Karl-Liebknecht-Str.\,24/25, 14476 Golm, Germany
\and Department of Physics and Astronomy, University of Leicester, University Road, Leicester, LE1 7RH, United Kingdom
\and CAS Key Laboratory of Space Astronomy and Technology, National Astronomical Observatories, Chinese Academy of Sciences, Beijing, 100012, P.R. China % 30
\and Australian Astronomical Observatory, PO Box 915, North Ryde, NSW 1670, Australia.
}
